The large scale clustering in dispersion measure space

### 2015-05-20 writeup/dm_space_distortions.tex
Many edits.

\documentclass[twocolumn,prl,nofootinbib]{revtex4-1}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}
\usepackage{verbatim}
\usepackage{times}
\usepackage{afterpage}
\usepackage{epstopdf}

@@

The clustering of matter on large scales has been
heralded as the next great probe the Universe after the cosmic microwave
background (CMB). The large-scale structure in principle contains far more
information than the CMB, because it can be studied in three dimensions.
Traditionally the redshift of spectral lines caused by the Hubble flow has
been employed to measure radial distance. Such redshift
surveys have now aggregated the positions of millions of galaxies into three
dimensional density maps, exposing a rich structure of clusters, filaments,
walls and voids.

% This paragraph needs to be reorganized.
However, redshift is not the only measure of radial distance. In particular,
dispersion of electromagnetic signals due to intervening plasma
is readily measured from fast radio bursts (FRB) which are a class
of radio transient first reported in \citet{2007Sci...318..777L}.
There have since been 
10 such bursts reported \citep{2012MNRAS.425L..71K,2013Sci...341...53T, 2014ApJ...790..101S, 2014ApJ...792...19B, 2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
per sky per day \cite{2015arXiv150500834R}. 
The dispersion measure
(DM) is a line-of-site integral of the free electron density and can thus be
used as a distance estimate, as is routinely done for galactic pulsars.
Because FRBs are observed to have dispersion measures greatly in excess of
the galactic expectation they must be of extra-galactic origin, with their
dispersion produced either by
inter-galactic medium (IGM) \citep{2013Sci...341...53T} or the
environment of the source
\citep{2014ApJ...785L..26L,2015arXiv150101341P}.
If the dispersion is dominated by the inter-galactic medium, then 
 then the average DM-distance relation can be modelled
\citep{2004MNRAS.348..999I, 2003ApJ...598L..79I} and the sources are at
cosmological distances of a few gigaparsecs. This would permit
the study of the clustering of FRBs in three dimensions which should trace the
large-scale structure of the Universe on linear scales.

Neither redshift nor dispersion measure are perfect proxies for radial distance.
Redshifts are systematically biased by the peculiar velocities of the object
relative to the Hubble flow. This leads to additional apparent clustering 
in redshift
space which was first calculated by \citet{1987MNRAS.227....1K}
using linear theory.
Similarly, distance estimates from dispersion measure will be biased by
inhomogeneities in the electron density \citep{2014ApJ...780L..33M},
again leading to additional apparent
clustering of sources in dispersion measure space.  In this letter we calculate
these DM space distortions and consider the detectability of the signal by
upcoming surveys.

@@

\emph{Dispersion measure space} is the three dimensional coordinates,
$\vec x_s$ inferred from the dispersion measure assuming that the electrons are
homogenious. This only affect the radial coordinate such that $\vec x_s = \hat
n \chi_s$ with $\chi_s$ defined by the equation
\begin{equation}
    {\rm DM}(\chi_s) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi').
\end{equation}

@@

We wish to relate the density of a tracer $f$ measured in DM space to its
density in real space. We follow the derivation in \citet{1987MNRAS.227....1K}
of the
redshift space distortions. Start by noting that the total number of tracers
in a volume element is the same in both spaces:
\begin{equation}
\label{e:density}
n_{fs}(\vec x_s) \ud^3\vec x_s = n_{f}(\vec x) \ud^3\vec x.
\end{equation}
We split the density into a homogeneous part plus perturbations,
\begin{equation}
    \bar{n}_{fs}(\chi_s)\left[ 1 + \delta_{fs}(\vec x_s)\right] \ud^3\vec x_s
    = \bar{n}_{f}(\chi)\left[ 1 + \delta_f(\vec x)\right] \ud^3\vec x.
\end{equation}
Averaged over the sky, the density should be the same in DM 
space as in real space,
\begin{equation}
\bar{n}_{fs}(\chi) = \bar{n}_f(\chi).
\end{equation}
Therefore,
\begin{align}
\bar{n}_{fs}(\chi_s) 
    &= \bar{n}_{f}(\chi) + (\chi_s - \chi)\frac{\ud \bar{n}_f}{\ud \chi}\\
    &= \bar{n}_{f}(\chi)
       + \frac{\ud \bar{n}_f}{\ud \chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi')
       \label{e:nfs}
\end{align}

The Jacobian in spherical coordinates is
\begin{align}
\left| \frac{\ud^3\vec x}{\ud^3\vec x_s} \right|
    &= \frac{\ud \chi}{\ud \chi_s}\frac{\chi^2}{\chi_s^2}\\
    &= (1 + \delta_e)^{-1}
       \left(1 + \frac{\int_0^\chi \ud \chi' \delta_e(\hat n \chi')}
                      {\chi}\right)^{-2}\\
    &\approx 1 - \delta_e
        - \frac{2}{\chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi')
        \label{e:jac}
\end{align}

@@

The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ arise since the
misinterpretation of the radial distance causes the observed tracer density to
be compared to the wrong background density. The $\frac{2}{\chi}$ term is
caused by a misinterpretation of angular distances when the radial distance is
mis measured.  Both terms are in-principle present in redshift space but are
negligible. Because radial velocities are only sourced by modes with large
radial wave vector, there is near perfect cancellation along the line of sight
and thus is very little net error in radial distance.

@@

Large-scale structure is usually studied through its two-point statistics, most
commonly the power-spectrum, $P(k)$.
Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
simple form in harmonic space. The equation's third term couples harmonic modes
and thus the two-point statistics cannot be phrased as a simple power spectrum.
We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
the cross-correlation angular power-spectrum of the DM space over-density,
on shells at $\chi$ and $\chi'$.
\begin{align}
    &\delta_{\ell\ell'}\delta_{mm'}C^{ss}_\ell(\chi, \chi') = \nonumber \\
    & \quad
        \left\langle
        \int\ud\Omega Y_{\ell m}(\hat n)
       \delta_{fs}(\hat n \chi, \chi)
        \int\ud\Omega' Y_{\ell' m'}(\hat n')
        \delta_{fs}(\hat n' \chi', \chi')
        \right\rangle
\end{align}
The first two term in Equation~\ref{e:delta_s} are stationary. For stationary,
isotropic, tracers $x$ and $y$ we have 
$\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
dependance, the angular cross power spectrum of such tracers is
\begin{align}
    %\delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
    %&= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
    %    \langle \delta_x(\hat n \chi) \delta_y(\hat n' \chi') \rangle,
    %    \\
    C^{xy}_\ell(\chi,\chi')
    &= \frac{2}{\pi}
\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k).
\end{align}
In reality the power spectrum evolves on the order of a Hubble time.
The angular cross-correlations will be very small unless $\chi$ and $\chi'$ are
within a few correlation lengths of one another, roughly a few hundred
megaparsecs.  The evolution of the power-spectrum is negligible over these time
differences which leads to a straight forward way to include the evolution of
the perturbations:
\begin{align}
C^{xy}_\ell(\chi,\chi') 
    \approx \frac{2}{\pi}
    \int_0^\infty\ud k k^2
    j_\ell(k\chi) j_{\ell}(k\chi')
    P_{xy}(k,(\chi + \chi')/2),\nonumber &\\
    |\chi - \chi'| \ll 1/aH.&
\end{align}

The thrid term in Equation~\ref{e:delta_s} is not stationary but is an integral
over the stationary field $\delta_e$.
Define $\delta_d$ as
\begin{equation}
    \delta_d(\hat n \chi) \equiv \int_0^\chi \ud \chi' \delta_e(\hat n \chi').
\end{equation}
It is straight-forward to show that
\begin{widetext}
\begin{equation}
C^{dd}_\ell(\chi,\chi')
    =
    \frac{2}{\pi}
    \int_0^\chi\ud\chi''
    \int_0^{\chi'}\ud\chi'''
    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
    P_{ee}(k, (\chi''+\chi''')/2).
\end{equation}

@@

Equation~\ref{e:Clss} can be simplified substantially by adopting the small
angle and Limber approximations \citep{1953ApJ...117..134L,
1992ApJ...388..272K, 1998ApJ...498...26K}.  The small angle
approximation eliminates the $k$ integral over spherical Bessel functions, replacing it
with a Fourier transform, and is valid for $\ell \gg 1$. The Limber
approximation assumes that only modes with small radial component of their wave
vector contribute to the radial integrals and is valid if the power spectra
evolve slowly compared to the correlation length \citep{2008PhRvD..78l3506L}
(which has already been
assumed). With these approximations we have
\begin{align}
    &C^{ss}_\ell(\chi, \chi') \approx
    \nonumber \\ & \quad
    \frac{1}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P_{[ee + ff - 2ef]}
        (\sqrt{k_\parallel^2 + \nu^2/\bar\chi^2}, \bar\chi)
    \nonumber \\ & \quad +
    A(\chi) A(\chi')
    \int_0^{\chi_{\rm min}}\ud\chi''
    \frac{1}{\chi^{\prime\prime 2}}
    P_{ee}(\nu/\chi'',\chi'')
    \nonumber \\ & \quad +
    \frac{A(\chi_{\max})}{\chi_{\min}^2}
    P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
    \label{e:Clss_limber}
\end{align}
where $\nu\equiv\ell + 1/2$, $\chi_{\min} \equiv \min(\chi, \chi')$,
and $\chi_{\max} \equiv \max(\chi,
\chi')$ .  We've found that these approximations are excellent for $\ell
\gtrsim 10$
and use this form for the remainder of the paper. In the above equation we dub
the three terms the `local', `integral' and `cross' terms respectively and will
refer to them as such for the remainder of this work.

\section{Modeling and measurement}

There are a number of effects that will complicate the measurement of the
above calculated angular power spectrum by a real survey of dispersion 
measures.  The first is
that the model that the free electron density decomposes into a homogeneous
part plus a random field of perturbations is not correct. Firstly, all signals
must pass through the Milky Way's galactic disk, halo and local environment
which will contribute to the dispersion measure. However, this is only a 
single function of $\hat n$  which can presumably be well
measured. In addition, this function could in principal be well characterized
by independent data such as observations of pulsars.  As such, it should be
possible to subtract the local
contribution, as was done in
\citet{2014arXiv1412.4829D}, and this is unlikely to be a limiting obstacle.

More concerning is the dispersion from the burst progenitor's environment
as well as the halo in which it resides. These electrons will presumably be
clustered around the burst progenitor on scales far smaller than DM-space
structure maps and thus are not accounted for in the $\delta_e$--$\delta_f$
correlations included in the above formalism.  This will have a mean
contribution, common to all bursts and which may be epoch dependant, which will
modify the mean DM--distance relation. This will need to be calibrated in some
why or else fit with nuisance parameters during parameter estimation.  There
will also be a stochastic piece which varies from burst to burst.  This will
limit the precision at which $\chi_s$ can be measured, thus limiting the
resolution of DM space density maps in the radial direction.

Detailed treatment of these complications is beyond the scope of the current
work. The magnitude of the contribution from the progenitor is at present
unconstrained by data. To crudely deal with it here we use relatively large 
$\chi$ bins of $100\,{\rm MPc}/h$ in sensitivity estimates.

The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
many spacial scales, small scales from smaller radial distance and larger
scales from greater distances. The mixing of scales complicates the
interpretation of measurements, since structure formation on scales smaller
than $\sim10\,{\rm MPc}/h$ is non-linear and hard to model. A similar issue
exists in the field of weak gravitational lensing, where the formula for the
angular power spectrum has a similar form.  However in lensing a kernel in
the line-of-sight integral, arising from geometric effects, suppresses the
contribution from small distances, partially alleviating the issue.

There is an advantage to the lack of kernel in the DM-space integral term.
Lensing tomography---the use of sources at multiple redshifts to unmix
spatial scales---is complicated by the kernel. The kernel's shape depends on
the source redshift, reweighting the line of sight and
making tomography inexact.  In contrast the integrand in the integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line of sight (and thus different
spatial scales) can be separated exactly. Again, a detailed study of DM space
tomography is beyond the scope of this work.  The avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm MPc}/h$ are well
measured by the correlations with these radial slices. We thus neglect the
information from these slices in our sensitivity measurements and ignore
contributions to the integral term from below this distance. The smallest
spatial scale that contributes the our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm MPc}$.

For plotting the DM space power-spectra we use a toy model for the electron and
FRB clustering that assumes both are biased tracers of the dark matter,
\emph{i.e.}~$P_{xy}(k)=b_x b_y P(k)$.  We
calculate the time dependant dark matter power-spectrum using {\tt CAMB} using
the integrated {\tt HALOFIT} to approximate the non-linear evolution. We assume
that the electron bias $b_e=1$, which should be true on large scales due to
approximate conservation of free electrons. The bias of FRB sources is
unconstrained by data and we choose it to be $b_f=1.3$. The coefficient
$A(\chi)$ depends on the density of detected FRB sources, $\bar n_f(\chi)$.
We use a simple model where all events above a fixed flux are detected,
the intrinsic luminosity function has the
\citet{1976ApJ...203..297S} form with index $-1$, and events at the cut off of the
luminosity function and at
a radial distance of $\chi=2350\,{\rm MPc}/h$ are at the detection threshold.
This source density is shown in Figure~\ref{f:n_f} with the resulting DM-space
power-spectrum in Figure~\ref{f:terms}.

@@

I can be seen in Figure~\ref{f:terms} that the integral term dominates the
cross term and the local term except at small radial separations.  We've found
that this is generically true for most $(\chi, \chi')$ pairs and that the
sensitivity shown in Figure~\ref{f:sensitivity} is dominated by the integral
term. Since the integral term only depends on the clustering of electrons, not
sources, an FRB survey could be used to study the distribution of electrons and
potentially solve the `missing baryon problem' as pointed out in
\citet{2014ApJ...780L..33M}.

We have calculated the clustering of sources in dispersion measure space and
shown that a survey detecting a modest $10^4$ fast radio bursts of cosmological
origin could detect the clustering signal.

Looking forward, DM-space
clustering could become a powerful probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It might even be possible to extract it from the integral
term using tomography.
This however depends on the contribution to dispersion measure from
the source's environment and host halo to be modest compared to the
contribution from the IGM.

>>>>

\documentclass[twocolumn,prl,nofootinbib,floatfix]{revtex4-1}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{color}
\usepackage{verbatim}
\usepackage{times}
\usepackage{afterpage}
\usepackage{epstopdf}

@@

The clustering of matter on large scales has been
heralded as the next great probe of the Universe after the cosmic microwave
background (CMB). The large-scale structure in principle contains far more
information than the CMB because it can be studied in three dimensions.
Traditionally the redshift of spectral lines, caused by the Hubble flow, has
been employed to measure radial distance and provide the third dimension.
Such redshift
surveys have now aggregated the positions of millions of galaxies into three
dimensional density maps, exposing a rich structure of clusters, filaments,
walls and voids.

However, redshift is not the only measure of radial distance. In particular,
dispersion of electromagnetic signals due to intervening plasma
is readily measured from fast radio bursts (FRB) which are a class
of radio transient first reported in \citet{2007Sci...318..777L}.
There have since been 
10 such bursts reported
\citep{2012MNRAS.425L..71K,2013Sci...341...53T,
2014ApJ...790..101S, 2014ApJ...792...19B, 
2015MNRAS.447..246P,2015ApJ...799L...5R} and total rate of bursts
been estimated to be $3.3^{+5}_{-2.5} \times 10^3$
per sky per day \cite{2015arXiv150500834R}. 
The dispersion measure
(DM) is a line-of-site integral of the free electron density and can thus be
used as a distance estimate, as is routinely done with galactic pulsars.
Because FRBs are observed to have dispersion measures greatly in excess of
the galactic expectation they must be of extra-galactic origin, with their
dispersion produced either by
inter-galactic medium (IGM) \citep{2013Sci...341...53T} or the
environment of the source
\citep{2014ApJ...785L..26L,2015arXiv150101341P}.
If the dispersion is dominated by the inter-galactic medium, then
then the average DM-distance relation can be modelled
\citep{2004MNRAS.348..999I, 2003ApJ...598L..79I} and the sources are at
cosmological distances of a few gigaparsecs. This would permit
the study of the clustering of FRBs in three dimensions which should trace the
large-scale structure of the Universe on linear scales.

Neither redshift nor dispersion measure are perfect proxies for radial distance.
Redshifts are systematically biased by the peculiar velocities of the object
relative to the Hubble flow. This leads to additional apparent clustering
in redshift
space which was first calculated by \citet{1987MNRAS.227....1K}
using linear theory.
Similarly, distance estimates from dispersion measure will be biased by
inhomogeneities in the electron density \citep{2014ApJ...780L..33M},
again leading to additional apparent
clustering of sources in dispersion measure space.  In this letter we calculate
these DM-space distortions and consider the detectability of the signal by
upcoming surveys.

@@

\emph{Dispersion measure space} is the three dimensional coordinates,
$\vec x_s$ inferred from the dispersion measure assuming that the electrons are
homogeneous. This only affect the radial coordinate such that $\vec x_s = \hat
n \chi_s$ with $\chi_s$ defined by the equation
\begin{equation}
    {\rm DM}(\chi_s) = \int_0^\chi \ud\chi' a(\chi')^2 \bar{n}_e(\chi').
\end{equation}

@@

We wish to relate the density of a tracer $f$ measured in DM space to its
density in real space. We follow the derivation in \citet{1987MNRAS.227....1K}
of the
redshift space distortions. Start by noting that the total number of tracers
in a volume element is the same in both spaces:
\begin{equation}
\label{e:density}
n_{fs}(\vec x_s) \ud^3\vec x_s = n_{f}(\vec x) \ud^3\vec x.
\end{equation}
We split the density into a homogeneous part plus perturbations,
\begin{equation}
    \bar{n}_{fs}(\chi_s)\left[ 1 + \delta_{fs}(\vec x_s)\right] \ud^3\vec x_s
    = \bar{n}_{f}(\chi)\left[ 1 + \delta_f(\vec x)\right] \ud^3\vec x.
\end{equation}
Averaged over the sky, $\langle \chi_s \rangle = \chi$ and thus `the density should
be the same in DM space as in real space,
\begin{equation}
\bar{n}_{fs}(\chi) = \bar{n}_f(\chi).
\end{equation}
Therefore,
\begin{align}
\bar{n}_{fs}(\chi_s) 
    &= \bar{n}_{f}(\chi) + (\chi_s - \chi)\frac{\ud \bar{n}_f}{\ud \chi}\\
    &= \bar{n}_{f}(\chi)
       + \frac{\ud \bar{n}_f}{\ud \chi}\int_0^\chi \ud \chi' \delta_e(\hat n
       \chi').
       \label{e:nfs}
\end{align}

The Jacobian in spherical coordinates is
\begin{align}
\left| \frac{\ud^3\vec x}{\ud^3\vec x_s} \right|
    &= \frac{\ud \chi}{\ud \chi_s}\frac{\chi^2}{\chi_s^2}\\
    &= (1 + \delta_e)^{-1}
       \left(1 + \frac{\int_0^\chi \ud \chi' \delta_e(\hat n \chi')}
                      {\chi}\right)^{-2}\\
    &\approx 1 - \delta_e
        - \frac{2}{\chi}\int_0^\chi \ud \chi' \delta_e(\hat n \chi').
        \label{e:jac}
\end{align}

@@

The $\frac{1}{\bar{n}_f}\frac{\ud \bar{n}_f}{\ud \chi}$ arise since the
misinterpretation of the radial distance causes the observed tracer density to
be compared to the wrong background density. The $\frac{2}{\chi}$ term is
caused by a misinterpretation of angular distances when the radial distance is
mismeasured.  In both cases analogous terms are in principle present in 
redshift space but are
negligible. Because radial velocities are only sourced by modes with large
radial wave vector, there is near perfect cancellation along the line of sight
and thus is very little net error in radial distance.

@@

Large-scale structure is usually studied through its two-point statistics, most
commonly the power spectrum, $P(k)$.
Unlike in redshift-space distortions, Equation~\ref{e:delta_s} does not have a
simple form in harmonic space. The equation's third term couples harmonic modes
and thus the two-point statistics cannot be phrased as a simple power spectrum.
We will instead use $C^{ss}_\ell(\chi,\chi')$, which is
the cross-correlation angular power spectrum of the DM-space over density,
on shells at $\chi$ and $\chi'$:
\begin{align}
    &\delta_{\ell\ell'}\delta_{mm'}C^{ss}_\ell(\chi, \chi') = \nonumber \\
    & \quad
        \left\langle
        \int\ud\Omega Y_{\ell m}(\hat n)
       \delta_{fs}(\hat n \chi, \chi)
        \int\ud\Omega' Y_{\ell' m'}(\hat n')
        \delta_{fs}(\hat n' \chi', \chi')
        \right\rangle.
\end{align}
The first two term in Equation~\ref{e:delta_s} are stationary. For stationary,
isotropic, tracers $x$ and $y$ we have 
$\langle \delta_x(\vec k, \chi) \delta_y(\vec k', \chi) \rangle = (2\pi)^3
\delta^3(\vec k - \vec k') P_{xy}(k, \chi)$.  If for a moment we ignore time
dependence, the angular cross-power spectrum of such tracers is
\begin{align}
    %\delta_{\ell\ell'}\delta_{mm'}C^{xy}_\ell(\chi, \chi')
    %&= \int\ud\Omega\ud\Omega'Y_{\ell m}(\hat n) Y_{\ell' m'}(\hat n')
    %    \langle \delta_x(\hat n \chi) \delta_y(\hat n' \chi') \rangle,
    %    \\
    C^{xy}_\ell(\chi,\chi')
    &= \frac{2}{\pi}
\int_0^\infty\ud k k^2 j_\ell(k\chi) j_{\ell}(k\chi')P_{xy}(k).
\end{align}
In reality the power spectrum evolves on the order of a Hubble time.
The angular cross correlations will be very small unless $\chi$ and $\chi'$ are
within a few correlation lengths of one another, roughly a hundred
megaparsecs.  The evolution of the power-spectrum is negligible over these time
differences which leads to a straight-forward way to include the evolution of
the perturbations:
\begin{align}
C^{xy}_\ell(\chi,\chi') 
    \approx \frac{2}{\pi}
    \int_0^\infty\ud k k^2
    j_\ell(k\chi) j_{\ell}(k\chi')
    P_{xy}(k,(\chi + \chi')/2),\nonumber &\\
    |\chi - \chi'| \ll 1/aH.&
\end{align}

The third term in Equation~\ref{e:delta_s} is not stationary but is an integral
over the stationary field $\delta_e$.
Define $\delta_d$ as
\begin{equation}
    \delta_d(\hat n \chi) \equiv \int_0^\chi \ud \chi' \delta_e(\hat n \chi').
\end{equation}
It is straight-forward to show that
\begin{widetext}
\begin{equation}
C^{dd}_\ell(\chi,\chi')
    =
    \frac{2}{\pi}
    \int_0^\chi\ud\chi''
    \int_0^{\chi'}\ud\chi'''
    \int_0^\infty\ud k k^2 j_\ell(k\chi'') j_{\ell}(k\chi''')
    P_{ee}(k, (\chi''+\chi''')/2).
\end{equation}

@@

Equation~\ref{e:Clss} can be simplified substantially by adopting the small
angle and Limber approximations \citep{1953ApJ...117..134L,
1992ApJ...388..272K, 1998ApJ...498...26K}.  The small angle
approximation eliminates the $k$ integral over spherical Bessel functions, replacing it
with a Fourier transform, and is valid for $\ell \gg 1$. The Limber
approximation assumes that only modes with small radial component of their wave
vector contribute to the radial integrals and is valid if the power spectra
evolve slowly compared to the correlation length \citep{2008PhRvD..78l3506L}
(which has already been
assumed). With these approximations we have
\begin{align}
    &C^{ss}_\ell(\chi, \chi') \approx
    \nonumber \\ & \quad
    \frac{1}{\bar\chi^2}
        \int_{-\infty}^\infty\frac{\ud k_\parallel}{(2 \pi)} 
        e^{i k_\parallel (\chi - \chi')}
        P_{[ee + ff - 2ef]}
        (\sqrt{k_\parallel^2 + \nu^2/\bar\chi^2}, \bar\chi)
    \nonumber \\ & \quad +
    A(\chi) A(\chi')
    \int_0^{\chi_{\rm min}}\ud\chi''
    \frac{1}{\chi^{\prime\prime 2}}
    P_{ee}(\nu/\chi'',\chi'')
    \nonumber \\ & \quad +
    \frac{A(\chi_{\max})}{\chi_{\min}^2}
    P_{[ee - ef]}(\nu/\chi_{\min}, \chi_{\min}),
    \label{e:Clss_limber}
\end{align}
where $\nu\equiv\ell + 1/2$, $\chi_{\min} \equiv \min(\chi, \chi')$,
and $\chi_{\max} \equiv \max(\chi,
\chi')$ .  We've found that these approximations are excellent for $\ell
\gtrsim 10$
and use this form for the remainder of the paper. In the above equation we dub
the three terms the `local', `integral' and `cross' terms respectively and will
refer to them as such henceforth.

\section{Modelling and measurement}

There are a number of effects that will complicate the measurement of the
above calculated angular power spectrum by a real survey of dispersion 
measures.  The first effect is
that the model that the free electron density decomposes into a homogeneous
part plus a random field of perturbations is not complete. Firstly, all signals
must pass through the Milky Way's galactic disk, halo, and local environment,
which will contribute to the dispersion measure. However, this is only a
single function of $\hat n$  which can presumably be well
measured. In addition, this function could in principle be well characterized
by independent data such as observations of pulsars.  As such, it should be
possible to subtract the local
contribution, as was done in
\citet{2014arXiv1412.4829D}, and this is unlikely to be a limiting obstacle.

More concerning is the dispersion from the source's environment
as well as the halo in which it resides. These electrons will presumably be
clustered around the source on scales far smaller than DM-space
structure map pixels and thus are not accounted for in the $\delta_e$--$\delta_f$
correlations included in the above formalism.  This will have a mean
contribution, common to all sources and which may be epoch dependant, which will
modify the mean DM--distance relation. This will need to be calibrated in some
why or else fit with nuisance parameters during parameter estimation.  There
will also be a stochastic piece which varies from source to source.  This will
limit the precision at which $\chi_s$ can be measured, thus limiting the
resolution of DM space density maps in the radial direction.

Detailed treatment of these complications is beyond the scope of the current
work. The magnitude of the contribution from the progenitor is at present
unknown. To crudely deal with it here we use relatively large 
$\chi$ bins of $100\,{\rm MPc}/h$ in sensitivity estimates.

The second term in Equation~\ref{e:Clss_limber} is an integral that mixes
many spatial scales, small scales from smaller radial distance and larger
scales from greater distances. The mixing of scales complicates the
interpretation of measurements, since structure formation on scales smaller
than $\sim10\,{\rm MPc}/h$ is non-linear and hard to model. A similar issue
exists in the field of weak gravitational lensing, where the formula for the
angular power spectrum has a similar form.  In lensing a kernel in
the line-of-sight integral, arising from geometric effects, suppresses the
contribution from small distances, partially alleviating the issue.

There is an advantage to the lack of kernel in the DM-space integral term.
Lensing tomography---the use of sources at multiple redshifts to unmix
spatial scales---is complicated by the kernel. The kernel's shape depends on
the source redshift, reweighting the line of sight integral and
making tomography inexact.  In contrast the integrand in the DM-space integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line of sight (and thus different
spatial scales) can be separated exactly. Again, a detailed study of DM space
tomography is beyond the scope of this work.  To avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm MPc}/h$ are well
measured by the correlations with these radial slices. We thus neglect the
information from these slices in our sensitivity measurements and ignore
contributions to the integral term from below this distance. The smallest
spatial scale that contributes the our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm MPc}$.

For plotting the DM-space power spectra we use a toy model for the electron and
FRB clustering that assumes both are biased tracers of the dark matter:
\emph{i.e.}~$P_{xy}(k)=b_x b_y P(k)$.  We
calculate the time dependant dark-matter power spectrum using {\tt CAMB} using
the integrated {\tt HALOFIT} to approximate the non-linear evolution. We assume
that the electron bias is $b_e=1$, which should be true on large scales due to
approximate conservation of free electrons. The bias of FRB sources is
unconstrained by data and we choose it to be $b_f=1.3$. The coefficient
$A(\chi)$ depends on the density of detected FRB sources, $\bar n_f(\chi)$.
We use a simple model where all events above a fixed flux are detected,
the intrinsic luminosity function has the
\citet{1976ApJ...203..297S} form with index $-1$, and events at the cut off of the
luminosity function and at
a radial distance of $\chi=2350\,{\rm MPc}/h$ are at the flux detection threshold.
This source density is shown in Figure~\ref{f:n_f} with the resulting DM-space
power-spectrum in Figure~\ref{f:terms}.

@@

It can be seen in Figure~\ref{f:terms} that the integral term dominates the
cross term and the local term except at small radial separations.  We've found
that this is generically true for most $(\chi, \chi')$ pairs and that the
sensitivity shown in Figure~\ref{f:sensitivity} is dominated by the integral
term. Since the integral term only depends on the clustering of electrons, not
sources, an FRB survey could be used to study the distribution of electrons and
potentially solve the `missing baryon problem' as pointed out in
\citet{2014ApJ...780L..33M}.

We have calculated the clustering of sources in dispersion measure space and
shown that a survey detecting $10^4$ fast radio bursts of cosmological
origin (as might be achieved by the CHIME FRB instrument) could detect the
clustering signal.
Looking forward, DM-space
clustering could become a powerful probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the contribution to dispersion measure from
the source's environment and host halo to be modest compared to the
contribution from the IGM.
